Reproducibility in Plant Pathology

### 2018-06-05 README.rmd

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)

>>>>

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
